Spatial Reasoning and Statistical Graphics

### 2014-11-03 Paper/Draft1/TestingVisualAptitude.Rnw
Remove STEM comment.

In addition to these tests, participants were asked to complete a questionnaire which includes questions about colorblindness, mathematical background, self-perceived verbal/mathematical/artistic skills, time spent playing video games, and undergraduate major. \comment{XXX should we classify majors into STEM/non-STEM? - there's a ton of literature and interest that we could potentially tap into \\\textit{I'm not opposed, but we have to decide where ag-majors fall... not everything is easily classifiable. Psychology is another problem: I was very STEM-psychology, but you don't have to be.}} These questions are designed to assess different factors which may influence a participant's skill at reading graphs and performing spatial tasks.

@@

\newtext{This emphasizes the underpinnings of lineups: they are a visual medium, but they ultimately are a classification task, presented in a graphical manner. Using lineups as a proxy for statistical significance tests is similar to using a classifier on pictoral data: while the data is presented ``graphically", the participant is actually classifying the data based on underlying summary statistics.}
\comment{that last sentance is probably reaching a bit far...}

>>>>

In addition to these tests, participants were asked to complete a questionnaire which includes questions about colorblindness, mathematical background, self-perceived verbal/mathematical/artistic skills, time spent playing video games, and undergraduate major. 
These questions are designed to assess different factors which may influence a participant's skill at reading graphs and performing spatial tasks.

@@

\newtext{This emphasizes the underpinnings of lineups: they are a visual medium, but they ultimately are a classification task, presented in a graphical manner. Using lineups as a proxy for statistical significance tests is similar to using a classifier on pictoral data: while the data is presented ``graphically", the participant is actually classifying the data based on underlying summary statistics.}
